### 2022-10-17 definitions.tex
up to date

\newcommand{\pred}{\textsc{Pred}}
\newcommand{\succ}{\textsc{Succ}}

@@

\begin{definition}
A {\em (resp. strongly) well-structured transition systems} (abbreviated as WSTS resp. SWSTS) 
is a TS
$(S, \rightarrow, \leq)$
equipped with a wqo ${\leq} \subseteq S \times S$ between states such that  
%  decidable ≤  wqo on S, i.e., for each two given states s, s ′ ∈ S, it is decidable whether s ≤ s ′ . 
the wqo is (resp. strongly) compatible with the transition relation, i.e., for all 
$s_1, t_1 , s_2 \in S$
	with $s_1 ≤ t_2$  and $s_1 \rightarrow s_2$ , there exists 
	$t_2 \in S$ with 
	$s_2 \leq t_2$ and $t_1 \rightarrow^{*} t_2$ 			
				(resp. $t_1 \rightarrow^{1} t_2$ ).
\end{definition}

@@

\problemx{TS $k$-resilience problem}
{A state $s$ of a TS $(S,\rightarrow)$, two disjoints subset of $S$ $SAFE$ and $BAD$.}
{$\forall s' \in BAD ~ (s \rightarrow^* s') \to \exists s'' \in SAFE ~ s' \rigtarrow^{\leq k} s''$ ?\newline}

@@

\problemx{TS bounded resilience problem}
{A state $s$ of a TS $(S,\rightarrow)$, two disjoints subset of $S$ $SAFE$ and $BAD$.}
{$\exists k \geq 0 ~ \forall s' \in BAD ~ (s \rightarrow^* s') \to \exists s'' \in SAFE ~ s' \rigtarrow^{\leq k} s''$ ?\newline}

@@

\problemx{WSTS $k$-resilience problem}
{A state $s$ of a WSTS $(S,\rightarrow)$, an ideal $I$ with a given basis, a decidable anti-ideal $J$.}
{$\forall s' \in J ~ (s \rightarrow^* s') \to \exists s'' \in I ~ s' \rigtarrow^{\leq k} s''$ ?\newline}

@@

\problemx{WSTS bounded resilience problem}
{A state $s$ of a WSTS $(S,,)$, an ideal $I$ with a given basis, a decidable anti-ideal $J$.}
{$\exists k \geq 0 ~ \forall s' \in J ~ (s \rightarrow^* s') \to \exists s'' \in I ~ s' \rigtarrow^{\leq k} s''$ ?\newline}

>>>>

\newcommand{\pred}{\textsc{Pred}}
\renewcommand{\succ}{\textsc{Succ}}

@@

\begin{definition}
A {\em (resp. strongly) well-structured transition systems} (abbreviated as WSTS resp. SWSTS) 
is a TS
$(S, \rightarrow, \leq)$
equipped with a wqo ${\leq} \subseteq S \times S$ between states such that  
%  decidable ≤  wqo on S, i.e., for each two given states s, s ′ ∈ S, it is decidable whether s ≤ s ′ . 
the wqo is (resp. strongly) compatible with the transition relation, i.e., for all 
$s_1, t_1 , s_2 \in S$
	with $s_1 \leq t_2$  and $s_1 \rightarrow s_2$ , there exists 
	$t_2 \in S$ with 
	$s_2 \leq t_2$ and $t_1 \rightarrow^{*} t_2$ 			
				(resp. $t_1 \rightarrow^{1} t_2$ ).
\end{definition}

@@

\problemx{TS $k$-resilience problem}
{A state $s$ of a TS $(S,\rightarrow)$, two disjoints subset of $S$ $SAFE$ and $BAD$.}
{$\forall s' \in BAD ~ (s \rightarrow^* s') \to \exists s'' \in SAFE ~ s' \rightarrow^{\leq k} s''$ ?\newline}

@@

\problemx{TS bounded resilience problem}
{A state $s$ of a TS $(S,\rightarrow)$, two disjoints subset of $S$ $SAFE$ and $BAD$.}
{$\exists k \geq 0 ~ \forall s' \in BAD ~ (s \rightarrow^* s') \to \exists s'' \in SAFE ~ s' \rightarrow^{\leq k} s''$ ?\newline}

@@

\problemx{WSTS $k$-resilience problem}
{A state $s$ of a WSTS $(S,\rightarrow, \leq)$, an upward-closed set $I$ with a given basis, a decidable downward-closed set $J$.}
{$\forall s' \in J ~ (s \rightarrow^* s') \to \exists s'' \in I ~ s' \rightarrow^{\leq k} s''$ ?\newline}

@@

\problemx{WSTS bounded resilience problem}
{A state $s$ of a WSTS $(S,\rightarrow, \leq)$, an upward-closed set $I$ with a given basis, a decidable downward-closed set $J$.}
{$\exists k \geq 0 ~ \forall s' \in J ~ (s \rightarrow^* s') \to \exists s'' \in I ~ s' \rightarrow^{\leq k} s''$ ?\newline}
